A fast global code motion algorithm for code size optimization

### 2019-03-22 paper.tex
correction
Update results for OpenCV

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{comment}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{graphviz}
\usepackage{auto-pst-pdf}
\usepackage{etoolbox}
\usepackage{flushend}
\usepackage{needspace}
\usepackage{algpseudocode}

@@

\begin{verbatim}
B0: b = m
    c = n
    if c is true then goto B3 else goto B4

@@

>>>>

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{comment}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{graphviz}
\usepackage{auto-pst-pdf}
\usepackage{etoolbox}
\usepackage{flushend}
\usepackage{needspace}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}

@@

\begin{verbatim}
B0: b = m
    c = n
    if c is true then goto B1 else goto B2

@@

We compiled a popular open source computer vision library, OpenCV. We used OpenCV performance tests and scripts provided by them to measure performance gain with \gcm{}. We compared performance for every test in different test suites. We observe some gains with minor regressions. Feature2D test suite resulted in performance gain of $1-2\%$ without any performance regression. Ratio of performance with \gcm{} for different test suites is shown in Figure~\ref{fig:opencv-perf-result}.

\begin{figure}[H]

\begin{subfigure}{0.4\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm]{calib-perf-result.png} 
\caption{Calib3D}
\label{fig:subim1}
\end{subfigure}
\begin{subfigure}{0.4\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm]{core-perf-result.png}
\caption{Core}
\label{fig:subim2}
\end{subfigure}

\begin{subfigure}{0.4\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm]{dnn-perf-result.png} 
\caption{dnn}
\label{fig:subim3}
\end{subfigure}
\begin{subfigure}{0.4\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm]{feature-perf-result.png}
\caption{Feature2D}
\label{fig:subim4}
\end{subfigure}

\begin{subfigure}{0.4\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm]{imgproc-perf-result.png} 
\caption{ImgProc}
\label{fig:subim5}
\end{subfigure}
\begin{subfigure}{0.4\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm]{objdetect-perf-result.png}
\caption{ObjDetect}
\label{fig:subim6}
\end{subfigure}

\begin{subfigure}{0.4\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm, center]{video-perf-result.png} 
\caption{Video}
\label{fig:subim7}
\end{subfigure}

\caption{Ratio of performance for OpenCV perf test with \gcm{}}
\label{fig:opencv-perf-result}
\end{figure}

We report decrease in size of libopencv\_core library by $0.17\%$. There is no regression observed in size of other libraries. We cross-compiled OpenCV for Android using Android ntk 16b. We report decrease in size in Figure~\ref{fig:opencv-android-size-result}.  Notably with \gcm{} we observed $0.4\%$ decrease in size for OpenCV machine learning library libopencv\_ml.so* and it's core library libopencv\_core.so*.

\begin{figure}[H]
\includegraphics[width=0.9\linewidth, height=8cm, center]{opencv-android-size-result.png} 
\caption{Percentage decrease in size of OpenCV libraries on Android with \gcm{}}
\label{fig:opencv-android-size-result}
\end{figure}
